PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reviewed time chunks for COPING-GLAD

What proportion is over a year?
```{r eval=FALSE, include=FALSE}

>>>>

Proportion of people signed up over one year ago
```{r eval=FALSE, include=FALSE}
dat.glad <- dat.glad %>%
  mutate(
    over_one_year_time_diff_sign_up_coping_numeric =
      as.numeric(
        if_else(time_diff_sign_up_coping > 365, 1, 0
                )
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    over_one_year_time_diff_sign_up_coping =
      recode_factor(
        over_one_year_time_diff_sign_up_coping_numeric,
        "0" = "Sign up under one year before COPING",
        "1" = "Sign up over one year before COPING"
      )
  )

table(dat.glad$over_one_year_time_diff_sign_up_coping)
```
